Fingerprinting \titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}

### 2018-11-08 paper.tex
Add author name and email
Fix typos in abstract

\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ang Wei Ming\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
Chan Liang Fei Jeremy\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor 
Ong Yong Siang\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor 
Tan Zhen Yong\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor 
Xu Chen\\
       \email{xuchen@u.nus.edu}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
    Device fingerprinting is a modern technique which, instead of using traditional user identifiers(e.g. cookies and local storage), leverages on existing information available from user's device.
    In this paper, we investigates the various state-of-the-art technologies for device fingerprinting and authentification systems that utilize such fingerprint information.We analyzes the trade-off between uniqueness of the identifier generated and ease of use for authentication. Lastly, we also build a simple authentification system that can be reused and extended in real-world web applications.
\end{abstract}

>>>>

\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ang Wei Ming\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
Chan Liang Fei Jeremy\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor 
Ong Yong Siang\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor 
Tan Zhen Yong\\
       \email{tan.zhenyong@u.nus.edu}
% 5th. author
\alignauthor 
Xu Chen\\
       \email{xuchen@u.nus.edu}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
    Device fingerprinting is a modern technique which, instead of using traditional user identifiers (e.g. cookies and local storage), leverages on existing information available from user's device.
    In this paper, we investigates the various state-of-the-art technologies for device fingerprinting and authentification systems that utilize such fingerprint information. We analyzes the trade-off between the uniqueness of the identifer generated and ease of use for authentication. Lastly, we also build a simple authentication system that can be reused and extended in real-world web applications.
\end{abstract}
